Experimentally informed site-specific substitution models deepen phylogenetic estimates of the divergence of viral lineages

### 2018-02-28 manuscript/manuscript.tex
fixed typo in comment so doc compiles

\subsection*{Models with stationary states estimated from natural sequences give similar results to ExpCM's}
The previous sections used ExpCM's, which are mutation-selection models that use site-specific amino-acid preferences that have been measured experiments.
However, there are other implementations of mutation-selection models that infer the amino-acid preferences from natural sequence data.
These models are generally implemented in a Bayesian framework, which avoids the overfitting problems associated with trying to make maximum-likelihood estimates of thousands of parameters giving the site-specific stationary states.
For example, the CAT model\jdbcomment{citation} implements site-specific stationary states for amino-acid substitution models by drawing the stationary state at each site from a mixture model of distinct, finite amino-acid profiles \jdbcomment{wording in preceding sentence might need some tweaking}.
However, the model most comparable to our ExpCM's is the mutation-selection model implemented in \texttt{phylobayes}, \jdbcomment{and referred to as MutSel.}
This \jbcomment{MutSel} model is mathematically identical to the ExpCM's except the amino-acid preferences are sampled from a Bayesian mixture models rather than derived from experiments\jdbcomment{The preceding might not be accurate either in the wording about Bayesian mixture models, or because the nucleotide frequency parameters might be different? Also might have site-specific $\omega_r$. Check these and adjust to be accurate.}
Like ExpCM's, these MutSel models still assume a single set of site-specific amino-acid preferences for the entire tree.

>>>>

\subsection*{Models with stationary states estimated from natural sequences give similar results to ExpCM's}
The previous sections used ExpCM's, which are mutation-selection models that use site-specific amino-acid preferences that have been measured experiments.
However, there are other implementations of mutation-selection models that infer the amino-acid preferences from natural sequence data.
These models are generally implemented in a Bayesian framework, which avoids the overfitting problems associated with trying to make maximum-likelihood estimates of thousands of parameters giving the site-specific stationary states.
For example, the CAT model\jdbcomment{citation} implements site-specific stationary states for amino-acid substitution models by drawing the stationary state at each site from a mixture model of distinct, finite amino-acid profiles \jdbcomment{wording in preceding sentence might need some tweaking}.
However, the model most comparable to our ExpCM's is the mutation-selection model implemented in \texttt{phylobayes}, \jdbcomment{and referred to as MutSel.}
This \jdbcomment{MutSel} model is mathematically identical to the ExpCM's except the amino-acid preferences are sampled from a Bayesian mixture models rather than derived from experiments\jdbcomment{The preceding might not be accurate either in the wording about Bayesian mixture models, or because the nucleotide frequency parameters might be different? Also might have site-specific $\omega_r$. Check these and adjust to be accurate.}
Like ExpCM's, these MutSel models still assume a single set of site-specific amino-acid preferences for the entire tree.
